Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-17 article/article.Rmd
Commit 2024-05-17 12:14

To create a unified trend for the long term change of the clear sky irradiance, we
simulated the values of AOD derived from those sources with Libradtran. For both, we
use the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
exponent, and we choose the SZA of $55^\circ$ as a representative value for all runs.

For the period 1993 -- 2005

For the period 2005 -- 2005 we used

>>>>

To create a unified trend for the long term change of the clear sky irradiance, we
simulated the values of AOD derived from those sources with Libradtran. For both, we
used the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
coefficients, and we choose the SZA of $55^\circ$ as a representative value for all runs.
For the first period, the alpha Ångström coefficient is $1.6$ and the beta
coefficient $0.086$ and $0.059$, for 1997 and 2005 respectively. By interpolating the
resulting clear sky irradiance, we have a trend of $+0.21\,\%$ per year.
For the period 2005 -- 2005 we used the mean monthly values from AERONET, with a
similar simulation scheme. We computed the trend of clear sky radiation for each
month of the year, which gave us a mean clear sky radiation trend of $+0.14\,\%$ per year.

### 2024-05-17 article/article.tex
Commit 2024-05-17 12:14

To create a unified trend for the long term change of the clear sky
irradiance, we simulated the values of AOD derived from those sources
with Libradtran. For both, we use the AOD at \(500\,\text{nm}\), which
was inferred by the available Ångström exponent, and we choose the SZA
of \(55^\circ\) as a representative value for all runs.

For the period 1993 -- 2005

For the period 2005 -- 2005 we used

>>>>

To create a unified trend for the long term change of the clear sky
irradiance, we simulated the values of AOD derived from those sources
with Libradtran. For both, we used the AOD at \(500\,\text{nm}\), which
was inferred by the available Ångström coefficients, and we choose the
SZA of \(55^\circ\) as a representative value for all runs. For the
first period, the alpha Ångström coefficient is \(1.6\) and the beta
coefficient \(0.086\) and \(0.059\), for 1997 and 2005 respectively. By
interpolating the resulting clear sky irradiance, we have a trend of
\(+0.21\,\%\) per year. For the period 2005 -- 2005 we used the mean
monthly values from AERONET, with a similar simulation scheme. We
computed the trend of clear sky radiation for each month of the year,
which gave us a mean clear sky radiation trend of \(+0.14\,\%\) per
year.
